Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2016-07-05 inst/examples/20160715-slides-Krakow.Rmd
moi

selected.places = c("Turku", "Uppsala", "Lund", "Stockholm")
df2 <- df0 %>% group_by(publication_decade, publication_place, catalog) %>%
               summarise(n = n()) %>%
	       filter(publication_place %in% selected.places) 
df2$catalog = factor(df2$catalog, levels = rev(c("Fennica", "Kungliga")))
df2$publication_place = droplevels(factor(df2$publication_place))
df3 = spread(df2, publication_decade, n, fill = 0)
df2 = melt(df3)
colnames(df2) = c("publication_place", "catalog", "publication_decade", "n")
df2$publication_decade = as.numeric(as.character(df2$publication_decade))
df2$n = as.numeric(as.character(df2$n))
for (catal in unique(df2$catalog)) {

>>>>

selected.places = c("Turku", "Uppsala", "Lund", "Stockholm")
df2 <- df0 %>% group_by(publication_decade, publication_place, catalog) %>%
               summarise(n = n()) %>%
	       filter(publication_place %in% selected.places) 
df2$catalog = factor(df2$catalog, levels = rev(c("Fennica", "Kungliga")))
df2$publication_place = droplevels(factor(df2$publication_place))
df3 = as.data.frame(spread(df2, publication_decade, n, fill = 0))
df2 = melt(df3)
colnames(df2) = c("publication_place", "catalog", "publication_decade", "n")
df2$publication_decade = as.numeric(as.character(df2$publication_decade))
df2$n = as.numeric(as.character(df2$n))
for (catal in unique(df2$catalog)) {
